---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# combcoint

<!-- badges: start -->
[![R-CMD-check](https://github.com/jens-klenke/combcoint/workflows/R-CMD-check/badge.svg)](https://github.com/jens-klenke/combcoint/actions)
<!-- badges: end -->

## Overview 

`combcoint` is package which provides, among other things, the _Combining non-cointegration tests_ of Bayer and Hanck. The following cointegration tests are implemented:

* `bayerhanck()` to perform the _Combining non-cointegration test_ which is implemented in two different versions, see the help file, with the command `?bayerhnack()` for more information
* `boswijk()` to perform the Boswijk cointegration test
* `banerjee()` to perform the banerjee cointregration test


## Installation

<!--
You can install the released version of combcoint from [CRAN](https://CRAN.R-project.org) with:

```{r eval = FALSE}
install.packages("combcoint")
```
-->

The development version can be downloaded from [GitHub](https://github.com/jens-klenke/combcoint) with:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("jens-klenke/combcoint")
```

## Usage

First install the package as described above

```{r, message = FALSE, eval = FALSE}
library(combcoint)

combcoint::bayerhanck(sp ~ ibm + ko, data = ibmspko)

```


## Reference 

Bayer, C. and Hanck, C. (2013). Combining non-cointegration tests. _Journal of Time Series Analysis_, 34(1), 83 -- 95. [https://doi.org/10.1111/j.1467-9892.2012.00814.x](https://doi.org/10.1111/j.1467-9892.2012.00814.x)

Boswijk, H. P. (1994), Testing for an unstable root in conditional and structural error correction models, _Journal of Econometrics_ 63(1), 37-60.
[https://www.sciencedirect.com/science/article/abs/pii/0304407693015609](https://www.sciencedirect.com/science/article/abs/pii/0304407693015609)

Johansen, S. (1988), Statistical analysis of cointegration vectors, _Journal of Economic Dynamics and Control_ 12(2-3), 231-254. [https://www.sciencedirect.com/science/article/abs/pii/0165188988900413](https://www.sciencedirect.com/science/article/abs/pii/0165188988900413)

Banerjee, A., Dolado, J. J. and Mestre, R. (1998), Error-correction Mechanism Tests for Cointegration in a Single-equation Framework, _Journal of Times Series Analysis_ 19(3), 267-283. [https://doi.org/10.1111/1467-9892.00091](https://doi.org/10.1111/1467-9892.00091)

Engle, R. and Granger, C. (1987), Co-integration and Error Correction: Representation, Estimation, and Testing, _Econometrica_ 55(2), 251-76. [https://doi.org/10.2307/1913236](https://doi.org/10.2307/1913236)
